---
title: "Proficiency test 2"
format: pdf
editor: visual
author:
  name: Vincent Zheng
---

## Task 1
```{r}
for (i in 1:3){
  print(mtcars$mpg[i])
}
```
## Task 2
```{r}
count_above <- function(vector, value){ #creates the function that takes two inputs
  count <- 0 #creates an object that acts as a counter
  for (i in 1:length(vector)){ #for loop that runs however long the vector is
    if (vector[i] > value){ #runs if the vector value is greater than the cutoff
      count <- count + 1 #increases the count object by 1
    }
  }
  return(count) #returns the count value
}
```

```{r}
count_above(iris$Sepal.Length, 6) 
count_above(mtcars$disp, 150)
```

## Task 3

Masking functions is when a package that was newly installed contains a function that shares a name with a function that has either existed in a previously installed package or the base r functions. As a result, if not specifically specified, when running the function name, the one that corresponds to the newest package will be ran. For example, if package 'w' has a function called 'g' and has been installed and package 'q' was installed after that also has a function named 'g', the function g from package q will be ran when it is called unless w was libraried in the code chunk.

## Task 4
```{r}
iris$Sepal.Length[1] #returns the sepal length of the first iris flower in the dataset
iris[1,1]
```

